### 2014-08-05 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor cleanup to table

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Reference  \\
\midrule
 Simulation Time                   &  5 min                                                        & -- \\[.25cm]
 Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature~\cite{NIOSH:Bowyer}              &  7~$^{\circ}$C (45~$^{\circ}$F)                                               & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
                                   &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$   & \\
                                   &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  & \\
                                   &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
                                   &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }   &  $k$: 0.12~\si{W/(m.K)})                                   & \multirow{3}{*}{Section~\ref{matl}} \\
                                   &  $\rho$: 510~kg/m$^3$                                      & \\
                                   &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                              & \\[.25cm]
\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   &  $\rho$: 810~kg/m$^3$                                      & \\ 
                                   &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                               & \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\begin{table}
\centering
\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
\begin{tabular}{lll}
\toprule[1.5pt]
Parameter & Description & Discussion  \\
\midrule
 Simulation Time                   &  5 min                                                        & -- \\[.25cm]
 Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
 Ambient Temperature             &  25~$^{\circ}$C (77~$^{\circ}$F)$^{*}$                                               & -- \\ [.1cm]
\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
                                   &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$   & \\
                                   &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  & \\
                                   &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
                                   &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }   &  $k$: 0.12~\si{W/(m.K)})                                   & \multirow{3}{*}{Section~\ref{matl}} \\
                                   &  $\rho$: 510~kg/m$^3$                                      & \\
                                   &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                              & \\[.25cm]
\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                   &  $\rho$: 810~kg/m$^3$                                      & \\ 
                                   &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                               & \\
\bottomrule[1.25pt]
\end{tabular}\par
$^{*}$ Initial interior temperatures were assumed to be 25~$^{\circ}$C, exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}
\end{table}
